Chord: A Versatile Platform for Program Analysis

### 2011-03-29 main/doc/datalog_analysis.tex
more documentation

\chapter{Datalog Analysis}
\label{chap:datalog-analysis}

@@

A Datalog analysis declares a bunch of input/output program relations,
each over one or more program domains, and provides a bunch of rules (constraints)
specifying how to compute the output relations from the input relations.
An example of such an analysis is shown in Figure \ref{fig:datalog-analysis}.

\begin{figure}
{\small
\begin{verbatim}
    # name=datarace-dlog

@@

    # Analysis constraints
    hasWrite(e1,e2) :- write(e1).
    hasWrite(e1,e2) :- write(e2).
    candidate(e1,e2) :- field(e1,f), field(e2,f), hasWrite(e1,e2), e1 <= e2.
    datarace(t1,e1,t2,e2) :- candidate(e1,e2), reach(t1,e1), reach(t2,e2), \
        alias(e1,e2), escape(e1), escape(e2), unguarded(t1,e1,t2,e2).
\end{verbatim}
}
\label{fig:datalog-analysis}
\caption{An Example Datalog Analysis.}
\end{figure}

@@

TODO

@@

\begin{verbatim}
    prompt> ant -Ddlog.file=<file> -Dwork.dir=<dir> solve
\end{verbatim}
where {\tt <file>} denotes the file defining the Datalog analysis
to be tuned, and {\tt <dir>} is the directory containing the
program domains ({\tt *.dom} files) and program relations ({\tt *.bdd} files)
consumed by the analysis (this is by default the
\code{chord_output/bddbddb/} directory generated
by a previous run of Chord.

@@

\begin{verbatim}
OUT> Rule VH(u:V0,h:H0) :- VV(u:V0,v:V1), VH(v:V1,h:H0), VHfilter
(u:V0,h:H0).
OUT>    Updates: 2871
OUT>    Time: 6798 ms
OUT>    Longest Iteration: 0 (0 ms)
OUT> Rule IM(i:I0,m:M0) :- reachableI(i:I0), specIMV(i:I0,m:M0,v:V0), VH(v:V0,_:H0).
OUT>    Updates: 5031
OUT>    Time: 6972 ms
OUT>    Longest Iteration: 0 (0 ms)
\end{verbatim}

@@

\begin{verbatim}
# V0:16 H0:12
# 14 15 16 17 18 19 20 21 22 23 24 25 26 27 28 29
# 82 83 84 85 86 87 88 89 90 91 92 93
28489 134
39 36 33 30 27 24 21 18 15 12 9 6 3 0 81 79 77 75 73 71 69 67 65 63 61 59 57 55  \
   53 51 82 80 78 76 74 72 70 68 66 64 62 60 58 56 54 52 37 34 31 28 25 22 19 16 \
   13 10 7 4 1 117 116 115 114 113 112 111 110 109 108 107 106 50 49 48 47 46 45 \
   44 43 42 41 40 105 104 103 102 101 100 99 98 97 96 95 94 93 92 91 90 89 88 87 \
   86 85 84 83 133 132 131 130 129 128 127 126 125 124 123 122 121 120 119 118   \
   38 35 32 29 26 23 20 17 14 11 8 5 2
287 83 0 1
349123 84 287 0
349138 85 0 349123
...
\end{verbatim}

>>>>

\xname{datalog_analysis}
\chapter{Datalog Analysis}
\label{chap:datalog-analysis}

@@

A Datalog analysis declares a bunch of input/output program relations,
each over one or more program domains, and provides a bunch of rules (constraints)
specifying how to compute the output relations from the input relations.
An example of such an analysis is shown below:

\texonly{\newpage}

\begin{framed}
{\small
\begin{verbatim}
    # name=datarace-dlog

@@

    # Analysis constraints
    hasWrite(e1,e2) :- write(e1).
    hasWrite(e1,e2) :- write(e2).
    candidate(e1,e2) :- field(e1,f), field(e2,f), hasWrite(e1,e2), e1 <= e2.
    datarace(t1,e1,t2,e2) :- candidate(e1,e2), reach(t1,e1), reach(t2,e2), \
        alias(e1,e2), escape(e1), escape(e2), unguarded(t1,e1,t2,e2).
\end{verbatim}
}
\end{framed}

@@

{\bf Under Construction}

@@

\begin{framed}
\begin{verbatim}
ant -Ddlog.file=<file> -Dwork.dir=<dir> solve
\end{verbatim}
\end{framed}

where {\tt <file>} denotes the file defining the Datalog analysis
to be tuned, and {\tt <dir>} is the directory containing the
program domains ({\tt *.dom} files) and program relations ({\tt *.bdd} files)
consumed by the analysis (this is by default the
\code{chord_output/bddbddb/} directory generated
by a previous run of Chord.

@@

\begin{framed}
\begin{verbatim}
OUT> Rule VH(u:V0,h:H0) :- VV(u:V0,v:V1), VH(v:V1,h:H0), VHfilter
(u:V0,h:H0).
OUT>    Updates: 2871
OUT>    Time: 6798 ms
OUT>    Longest Iteration: 0 (0 ms)
OUT> Rule IM(i:I0,m:M0) :- reachableI(i:I0), specIMV(i:I0,m:M0,v:V0), VH(v:V0,_:H0).
OUT>    Updates: 5031
OUT>    Time: 6972 ms
OUT>    Longest Iteration: 0 (0 ms)
\end{verbatim}
\end{framed}

@@

\begin{framed}
\begin{verbatim}
# V0:16 H0:12
# 14 15 16 17 18 19 20 21 22 23 24 25 26 27 28 29
# 82 83 84 85 86 87 88 89 90 91 92 93
28489 134
39 36 33 30 27 24 21 18 15 12 9 6 3 0 81 79 77 75 73 71 69 67 65 63 61 59 57 55  \
   53 51 82 80 78 76 74 72 70 68 66 64 62 60 58 56 54 52 37 34 31 28 25 22 19 16 \
   13 10 7 4 1 117 116 115 114 113 112 111 110 109 108 107 106 50 49 48 47 46 45 \
   44 43 42 41 40 105 104 103 102 101 100 99 98 97 96 95 94 93 92 91 90 89 88 87 \
   86 85 84 83 133 132 131 130 129 128 127 126 125 124 123 122 121 120 119 118   \
   38 35 32 29 26 23 20 17 14 11 8 5 2
287 83 0 1
349123 84 287 0
349138 85 0 349123
...
\end{verbatim}
\end{framed}

### 2011-03-29 main/doc/user_guide.tex
added BDD representation documentation
cleaned up and updated documentation
added more documentation
more documentation
new documentation
documentation

\documentclass{article}
\usepackage{html}
\usepackage{hyperref}

\oddsidemargin=0in
\evensidemargin=0in
\textwidth=6.0in
\textheight=8.0in

\html{\def\code#1{{\tt {#1}}}}
\latex{\def\code#1{\path{#1}}}
\def\url#1{\htmladdnormallink{#1}{#1}}
\def\Mdom{{\bf M}}
\def\Idom{{\bf I}}
\def\Vdom{{\bf V}}
\def\Zdom{{\bf Z}}
\def\Hdom{{\bf H}}
\def\Edom{{\bf E}}
\def\Fdom{{\bf F}}
\def\Cdom{{\bf C}}
\def\Tdom{{\bf T}}
\def\Pdom{{\bf P}}

\def\instM{{\bf instM}}
\def\statM{{\bf statM}}
\def\MH{{\bf MH}}
\def\MI{{\bf MI}}
\def\ME{{\bf ME}}

\def\cha{{\bf cha}}
\def\sub{{\bf sub}}
\def\HT{{\bf HT}}
\def\VT{{\bf VT}}
\def\EF{{\bf EF}}
\def\writeE{{\bf writeE}}

\def\virtIM{{\bf virtIM}}
\def\statIM{{\bf statIM}}
\def\specIM{{\bf specIM}}

\def\MmethArg{{\bf MmethArg}}
\def\MmethRet{{\bf MmethRet}}
\def\IinvkArg{{\bf IinvkArg}}
\def\IinvkRet{{\bf IinvkRet}}
\def\MordMethArg{{\bf MordMethArg}}
\def\MspcMethArg{{\bf MspcMethArg}}

\def\MobjVarAsgnInst{{\bf MobjVarAsgnInst}}
\def\MclsVarAsgnInst{{\bf MclsVarAsgnInst}}
\def\MobjValAsgnInst{{\bf MobjValAsgnInst}}
\def\MgetInstFldInst{{\bf MgetInstFldInst}}
\def\MputInstFldInst{{\bf MputInstFldInst}}
\def\MgetStatFldInst{{\bf MgetStatFldInst}}
\def\MputStatFldInst{{\bf MputStatFldInst}}

\def\syncMV{{\bf syncMV}}
\def\nestedLocks{{\bf nestedLocks}}

\def\VH{{\bf VH}}
\def\FH{{\bf FH}}
\def\HFH{{\bf HFH}}
\def\IM{{\bf IM}}

\def\forkC{{\bf forkC}}

\def\CVC{{\bf CVC}}
\def\FC{{\bf FC}}
\def\CFC{{\bf CFC}}
\def\CICM{{\bf CICM}}
\def\CHC{{\bf CHC}}

\def\clinitM{{\bf clinitM}}

\def\bddbddb{{\tt bddbddb}}
\def\Chord{Chord}

\def\NameToTrgtMap{{\tt NameToTrgtMap}}
\def\NameToTaskMap{{\tt NameToTaskMap}}
\def\ConsumedNameToTasksMap{{\tt ConsumedNameToTasksMap}}
\def\TaskGraph{{\tt TaskGraph}}
\def\TaskMapEntries{{\tt TaskMapEntries}}
\def\TrgtMapEntries{{\tt TrgtMapEntries}}
\def\DlogMapEntries{{\tt DlogMapEntries}}
\def\Tasks{{\tt Tasks}}
\def\Trgts{{\tt Trgts}}
\def\ValidTasks{{\tt ValidTasks}}
\def\TrgtNames{{\tt TrgtNames}}

\title{Chord: A Static and Dynamic Program Analysis Framework for Java}
\author{Mayur Naik}
\date{\today}
\begin{document}
\maketitle

\input{whatis_chord}
\newpage
\input{download_and_installation}
\newpage
\input{program_setup}
\newpage
\input{building_scope}
\newpage
\input{running_analysis}
\newpage
\input{writing_analysis}
\newpage
\input{writing_dynamic_analysis}
\newpage
\input{instr_events}
\newpage
\input{writing_datalog_analysis}
\newpage
\input{tuning_datalog_analysis}
\newpage
\input{program_representation}
\newpage
\input{pointsto}
\newpage
\input{datarace}
\newpage
\input{deadlock}
\newpage
\input{chord_sysprops}
\newpage
\input{acknowledgments}

>>>>

\documentclass[openany]{book}
\usepackage{hyperlatex}
\usepackage{hyperref}
\texonly{
	\usepackage{graphicx}
	\usepackage{framed}
}

\texonly{
% put borders around figures
	%\usepackage{float}
	%\floatstyle{boxed} 
	%\restylefloat{figure}
% set dimensions of page/text
	\parindent=0in
	\parskip=10pt
	\oddsidemargin=-0.3in
	\evensidemargin=-0.3in
	\textwidth=7in
	\textheight=8.0in
% redefine certain commands
	\renewcommand\code[1]{\path{#1}}
	\renewcommand\xlink[2]{\href{#2}{#1}}
}

\htmlonly{
	\newcommand\code[1]{{\tt #1}}
	\newcommand\url[1]{\xlink{#1}{#1}}
	\newenvironment{framed}{\xmlattributes*{table}{border=1 frame=box rules=none cellpadding=8}\begin{tabular}{l}}{\end{tabular}}
}

\newcommand\javadoc[2]{\xlink{\code{#1}}{http://chord.stanford.edu/javadoc/#2}}

\newenvironment{mytable}[1]
	{\htmlattributes*{table}{border=1 cellpadding=10}\begin{tabular}{#1}}
	{\end{tabular}}

\newcommand\bh{{\bf h}}
\newcommand\bi{{\bf i}}
\newcommand\bo{{\bf o}}
\newcommand\bt{{\bf t}}
\newcommand\bm{{\bf m}}
\newcommand\be{{\bf e}}
\newcommand\bg{{\bf f}}
\newcommand\bb{{\bf b}}
\newcommand\bl{{\bf l}}
\newcommand\bp{{\bf p}}
\newcommand\br{{\bf r}}
\newcommand\bw{{\bf w}}

\setcounter{htmldepth}{2}
\setcounter{htmlautomenu}{3}

\htmltitle{Chord}
\htmladdress{mhn@cs.stanford.edu}

\title{Chord: A Versatile Platform for Program Analysis}
\author{Mayur Naik}
\date{\today}
\begin{document}
\maketitle

\input{whatis_chord}
\input{getting_started}
\input{example}
\input{architecture}
\input{properties}
\input{predefined_analyses}
\input{analyses}
\input{dynamic_analysis}
\input{datalog_analysis}
\input{computing_scope}
\input{program_representation}
\input{acknowledgments}
